---
title: "p8105_hw1_yk2959"
output: html_document
date: "2022-09-19"
---

## Problem 1
#### Loading and exploring the dataset

I have used the code provided and ran the code directly in the console to download the package containing the penguins dataset.

```{r}
install.packages("palmerpenguins")
```


*Next, I will use the following code to load and explore the penguins dataset.* 

```{r}
library(tidyverse)
library(knitr)

data("penguins", package = "palmerpenguins")

str(penguins)

View(penguins$species)
View(penguins$island)

nrow(penguins)
ncol(penguins)
```

__This dataset contains the following variables__ 

1. species: factor with 3 levels, "Adelie","Chinstrap", and "Gentoo"
2. island: factor with 3 levels, "Biscoe","Dream" and "Torgersen"
3. bill length (mm): numerical variable  
4. bill depth: (mm): numerical variable  
5. flipper length: integer variable 
6. body mass (g): integer variable
7. sex: factor with 2 levels, "female" and "male"
8. year: integer variable

NUMBER OF OBSERVATIONS

__The dataset has 344 rows and 8 columns.__
__There are 344 observations and 8 variables.__


__Mean flipper length is 200.9152mm based on the following code:__

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

#### Make a scatterplot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)

```

## Problem 2
Here is the dataset prob2_df that I created.
```{r}
prob2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  charac_vec = c("one","two","three","four","five","six","seven", "eight","nine","ten"), 
  factor_vec = factor(c("Happy", "Sad", "Mad", "Happy", "Sad", "Mad", "Happy", "Sad", "Mad", "Happy"))
  )

str(prob2_df)
```
* Calculating mean for norm_sample, a random sample of size 10 from a standard Normal distribution:
```{r}
mean(prob2_df$norm_samp)
```
__This works as the vector is numerical!__

* Calculating mean for  norm_samp_pos, a logical vector indicating whether elements of the sample are greater than 0:
```{r}
mean(prob2_df$norm_samp_pos)
```
__This works as the vector is logical!__

* Calculating mean for  charac_vec, a character vector of length 10:
```{r}
mean(prob2_df$charac_vec)
```
__This does not works as this is a character variable!__

* Calculating mean for  factor_vec, a factor vector of length 10, with 3 different factor “levels”:
```{r}
mean(prob2_df$factor_vec)
```
__This does not works as this is a character variable!__
