---
title: "p8105_hw1_yk2959"
output: html_document
date: "2022-09-19"
---

## Problem 1
#### Loading and exploring the dataset

I have used the code provided and ran the code directly in the console to download the package containing the penguins dataset.

*Next, I will use the following code to load and explore the penguins dataset.* 

```{r}
library(tidyverse)
library(knitr)

data("penguins", package = "palmerpenguins")

str(penguins)

View(penguins$species)
View(penguins$island)

nrow(penguins)
ncol(penguins)
```

__This dataset contains the following variables__ 

1. species: factor with 3 levels, "Adelie","Chinstrap", and "Gentoo"
2. island: factor with 3 levels, "Biscoe","Dream" and "Torgersen"
3. bill length (mm): numerical variable  
4. bill depth: (mm): numerical variable  
5. flipper length: integer variable 
6. body mass (g): integer variable
7. sex: factor with 2 levels, "female" and "male"
8. year: integer variable

__The dataset has 344 rows and 8 columns.__

__Mean flipper length is 200.9152mm based on the following code:__

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

#### Make a scatterplot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```
*Scatterplot not generated and cannot be saved*

## Problem 2



